A Data-Driven Framework for Neural Field Modeling

### 2011-01-04 ltx/first_order_framework/response_to_reviews.tex

        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.

\emph{To address this point, we have added an extra appendix with a derivation of the sampling theorem with the appropriate cross-referencing to the main text. An effort was made to keep this derivation minimal and as clear as possible. We have also added the references to relevant part of the text (that should have been there before, as the reviewer has correctly pointed out). We felt that it was worth adding the extra appendix to provide a clear derivation that is contextually and notationally relevant to this paper, as the derivations cited papers may not be clear to the Neuroimage general audience.}

        \item The existing literature on inversion schemes for similar models of brain activity.

        \item In section 3, Table 6 is mentioned however there is no such table in the ms.\\
\emph{The cross-referencing has been corrected.}
    \end{enumerate}

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed error in  xcorr analysis
fix some errors in the xcorr derivation

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}\right)\right] \\
	&= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}_n\right)\right) \right], \label{eq:ObsXCorr}

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_{t+1}\left(\mathbf{r}'\right)\, d\mathbf{r}'} \right].

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{m\left(\mathbf{r}-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} + e_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'} \right] \\	
	 &= \xi\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{ m\left(\mathbf{r} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) d\mathbf{r}'} \right] \nonumber \\
	&+ T_s\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega} {m\left(\mathbf{r} - \mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'} \right] \nonumber \\
	&+ \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega} { m\left(\mathbf{r} - \mathbf{r}'\right) e_t \left(\mathbf{r}'\right)\, d\mathbf{r}' } \right]

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r} + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{m\left(\mathbf{r}-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}'\right) +T_s \int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''} \right)\, d\mathbf{r}'} \right] \\
	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}}M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) F(\boldsymbol{\nu}) \right) \right\} \right]
where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform. Now we assume that sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function

@@

Furthermore, we assume the field is in the linear region of the piecewise function for the majority of the time. From this we get the simplified cross-correlation function

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi M(\boldsymbol{\nu})V(\boldsymbol{\nu}) + T_s M(\boldsymbol{\nu}) W(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu})  \right) \right\} \right] \\
	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \left(\xi  + T_s \varsigma W(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r}) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \right] \\
	&= \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \label{eq:xcorr_with_autocorr}

@@

where $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function.

To show how we get this result, we define the auto-correlation of the observations as
\begin{align}
	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right)y_{t}\left(\mathbf{r}\right)\right]\\
	&= \mathbf{E}\left[m(\mathbf{r} + \boldsymbol{\tau}) \ast v(\mathbf{r}) \times m(\mathbf{r}) \ast v(\mathbf{r})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \right\}\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
	&= \mathbf{E}\left[\mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})M(\boldsymbol{\nu})M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast V(\boldsymbol{\nu}) \right\}\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
	&= \mathbf{E}\left[m(\mathbf{r}+\boldsymbol{\tau}) \ast m(\mathbf{r}) \ast v^2(\mathbf{r})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2
\end{align}

Now to isolate the kernel, the Fourier transform is taken

@@

	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \left(\xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r})\right) \right\} \\
	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{ \xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}) \right\}.

@@

Now rearranging (Note: this step is wrong. The RHS should be a function of $\boldsymbol\tau$!)

@@

	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}) \right\}.

@@

	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} &\approx \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}) % \\
	 % 	(\varsigma T_s)^{-1} \mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}} {\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} - (\varsigma T_s)^{-1}\xi &\approx w(\mathbf{r})

@@

	II-C & $\theta_0$ & $110$ & $98.90$ & $16.48$ & $10.1$ \\
	& $\theta_1$ & -80 & $-73.13$ & $11.72$ & $ 8.58$ \\
	& $\theta_2$ & 5 & $4.37$ & $0.54$ & $12.6$ \\
	& $\xi$ & 0.9 & $0.925$ & $0.003$ & $2.78$ \\ \hline
\end{tabular}\label{tab:MexicanHatKernelResults}
\caption{\textbf{Results from varying the Mexican hat connectivity kernel parameters}}
\end{table*}
\clearpage
\newpage
\begin{table*}[!ht]
\begin{tabular}{c|ccccc}
	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
	II-D &$\theta_0$ & $15$ & $35.68$ & $16.72$ & $137.87$ \\
	& $\theta_1$ & 0 & $-18.16$ & $11.77$ & - \\
	& $\theta_2$ & 0 & $0.81$ & $0.53$ & - \\
	& $\xi$ & 0.9 & 0.923 & $0.002$ & 2.56 \\ \hline

@@

	II-F & $\theta_0$ & $50$ & $61.46$ & $11.51$ & $22.92$ \\
	& $\theta_1$ & 0 & $-15.03$ & $7.56$ & - \\
	& $\theta_2$ & 0 & $0.27$ & $0.29$ & - \\
	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
\end{tabular}\label{tab:GaussianKernelResults}
\caption{\textbf{Results from varying the Gaussian connectivity kernel parameter}}
\end{table*}

>>>>

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \\
	&= \mathbf{E}\left[\left(m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) + \boldsymbol{\varepsilon}_t\left(\mathbf{r}\right) \right) \times \left( m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right], \label{eq:ObsXCorr}

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right].

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left( \xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) + e_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \\	
	 &= \xi \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \nonumber \\
	&+ T_s\mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \nonumber \\
	&+ \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast e_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right) \right]
Now we assume that sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function

@@

Furthermore, we assume the field is in the linear region of the piecewise function for the majority of the time. 
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \varsigma v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right) \right]
Now we take the Fourier transform of the terms inside the expectation giving

@@

	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) + T_s e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \left(\xi + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \ast \left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \\
	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \right] \ast \mathbf{E}\left[\left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \label{eq:xcorr_pre_sub}

@@

where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform and $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function.

We define the auto-correlation of the observations as

@@

	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]\\
	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2

@@

Rearrange to get
\begin{equation}\label{eq:autocorr_for_sub}
	R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 = \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right].
Now to isolate the kernel equation~\ref{eq:autocorr_for_sub} is substituted into equation~\ref{eq:xcorr_pre_sub} and the Fourier transform is taken giving
	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \mathbf{E} \left[ \xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right] \right\} \\
	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right) \sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{\mathbf{E}[ \xi \delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) ]\right\}.
Now rearranging

@@

	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \mathbf{E}[ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) ]\right\}.

@@

	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} \approx \mathbf{E}[\xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau})].

@@

	II-C & $\theta_0$ & $110$ & $98.90$ & $16.48$ & $10.1$ \\
	& $\theta_1$ & -80 & $-73.13$ & $11.72$ & $ 8.58$ \\
	& $\theta_2$ & 5 & $4.37$ & $0.54$ & $12.6$ \\
	& $\xi$ & 0.9 & $0.925$ & $0.003$ & $2.78$ \\ \hline
\end{tabular}
\caption{\textbf{Results from varying the Mexican hat connectivity kernel parameters}}
\label{tab:MexicanHatKernelResults}
\end{table*}
\clearpage
\newpage
\begin{table*}[!ht]
\begin{tabular}{c|ccccc}
	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline
	II-D &$\theta_0$ & $15$ & $35.68$ & $16.72$ & $137.87$ \\
	& $\theta_1$ & 0 & $-18.16$ & $11.77$ & - \\
	& $\theta_2$ & 0 & $0.81$ & $0.53$ & - \\
	& $\xi$ & 0.9 & 0.923 & $0.002$ & 2.56 \\ \hline

@@

	II-F & $\theta_0$ & $50$ & $61.46$ & $11.51$ & $22.92$ \\
	& $\theta_1$ & 0 & $-15.03$ & $7.56$ & - \\
	& $\theta_2$ & 0 & $0.27$ & $0.29$ & - \\
	& $\xi$ & 0.9 & $0.924$ & $0.003$ & $2.67$ \\ \hline
\end{tabular}
\caption{\textbf{Results from varying the Gaussian connectivity kernel parameter}}
\label{tab:GaussianKernelResults}
\end{table*}
